Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-08-25 ising/Fibonacci/about.tex

%\important{Definition:} A curve diagram is...

@@

        $$ b(i_1, f_1), b(i_2, f_2), ... b(i_N, f_N) $$

@@

\important{Theorem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of local moves such that % DIAGRAM
$g = \phi f i.$

\important{Proof:}

@@

let $h_k = g_k + f_k.$
This is a simple closed curve in $D$...

>>>>

DIAGRAM

@@

        $$ b(i_1, f_1),\ b(i_2, f_2),\ ...\ b(i_N, f_N) $$

@@

\important{Problem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of local moves such that % DIAGRAM
$g = \phi f i.$

\important{Solution:}

@@

let $h_k = g_k + f_k.$
This is a simple closed curve in $D$ which splits $D$
into two regions, the inside (simply connected) and the
outside.
We find six cases, which we can distinguish between
using the winding number and whether the end points
of $f$ are inside or outside:

\heading{Combinatorial formulation}

We discretize the prolem for software implementation...

\heading{Numerical results}
